\documentclass[twoside,openright,titlepage,fleqn,
headinclude,11pt,a4paper,BCOR5mm,footinclude ]{scrbook}
%--------------------------------------------------------------
        \newcommand{\myTitle}{Analisi di reti metaboliche basata su
          propriet\`a di connessione\xspace}
% use the right myDegree option
\newcommand{\myDegree}{Corso di Laurea in Informatica\xspace}
%\newcommand{\myDegree}{
	%Corso di Laurea Specialistica in Scienze e Tecnologie 
	%dell'Informazione\xspace}
\newcommand{\myName}{Massimo Nocentini\xspace}
\newcommand{\myProf}{Pierluigi Crescenzi\xspace}
\newcommand{\myOtherProf}{Nome Cognome\xspace}
\newcommand{\mySupervisor}{Nome Cognome\xspace}
\newcommand{\myFaculty}{
	Facolt\`a di Scienze Matematiche, Fisiche e Naturali\xspace}
\newcommand{\myDepartment}{
	Dipartimento di Sistemi e Informatica\xspace}
\newcommand{\myUni}{\protect{
	Universit\`a degli Studi di Firenze}\xspace}
\newcommand{\myLocation}{Firenze\xspace}
\newcommand{\myTime}{Anno Accademico 2010-2011\xspace}
\newcommand{\myVersion}{Version 0.1\xspace}
%--------------------------------------------------------------
\usepackage[latin1]{inputenc} 
\usepackage[T1]{fontenc} 
\usepackage[square,numbers]{natbib} 
\usepackage[fleqn]{amsmath}  
\usepackage[english]{babel}
%--------------------------------------------------------------
\usepackage{dia-classicthesis-ldpkg} 
%--------------------------------------------------------------
% Options for classicthesis.sty:
% tocaligned eulerchapternumbers drafting linedheaders 
% listsseparated subfig nochapters beramono eulermath parts 
% minionpro pdfspacing
\usepackage[eulerchapternumbers,subfig,beramono,eulermath,
	parts]{classicthesis}
%--------------------------------------------------------------
\newlength{\abcd} % for ab..z string length calculation
% how all the floats will be aligned
\newcommand{\myfloatalign}{\centering} 
\setlength{\extrarowheight}{3pt} % increase table row height
\captionsetup{format=hang,font=small}
%--------------------------------------------------------------
% Layout setting
%--------------------------------------------------------------
\usepackage{geometry}
\geometry{
	a4paper,
	ignoremp,
	bindingoffset = 1cm, 
	textwidth     = 13.5cm,
	textheight    = 21.5cm,
	lmargin       = 3.5cm, % left margin
	tmargin       = 4cm    % top margin 
}
%--------------------------------------------------------------
\usepackage{listings}
\usepackage{hyperref}
% My Theorem
\newtheorem{oss}{Observation}[section]
\newtheorem{exercise}{Exercise}[section]
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}

\newtheorem{lem}[thm]{Lemma}

\newcommand{\vect}[1]{\boldsymbol{#1}}

% questo comando e' relativo alle correzioni che puo
% apportare il prof se lo desidera.
\newcommand{\prof}[1]{\boldsymbol{#1}}

% instead of boldsymbol I can use the arrow above the letter with
%\newcommand{\vect}[1]{\vec{#1}}

% page settings
% \pagestyle{headings}
%--------------------------------------------------------------
\begin{document}
\frenchspacing
\raggedbottom
\pagenumbering{roman}
\pagestyle{plain}
%--------------------------------------------------------------
% Frontmatter
%--------------------------------------------------------------
%\include{titlePage}
\pagestyle{scrheadings}
%--------------------------------------------------------------
% Mainmatter
%--------------------------------------------------------------
\pagenumbering{arabic}

% settings for the lstlisting environment
\lstset{
	language = java
	, numbers = left 
	, basicstyle=\sffamily%\footnotesize
	%, frame=single
	, tabsize=2
	, captionpos=b
	, breaklines=true
	, showspaces=false
	, showstringspaces=false
}
\chapter*{Report of activity: ``Architetture e metodi per la 
cooperazione applicativa'' }
Florence, \today
\\\\
This is the final document that describes the state of the project
under the scholarship ``Architetture e metodi per la cooperazione
applicativa'', renewed in date $25/12/13$.  The work is supervised by
Prof. Enrico Vicario, the study of fluid dynamics equations and
optimizations is due to Fabio Tarani and the implementation of those
concepts is due to Massimo Nocentini.
\\\\
The work in this second period covers four main branches, namely we
have $(i)$ continued the collaboration with Terranova Software, $(ii)$
enhanced the fluid dynamic engine to support water contexts, $(iii)$
built a scheduler for the engine and finally $(iv)$ started a
maintenance process for the Oris1.0 project. In the following we
describe each of these four activities in greater details:
\begin{description}
\item[tuning the engine] the joint work with Terranova Software allows
  us to carefully test and tune the fluid dynamic engine, paying
  special attention to bug fixing and optimization. In fact two main
  issues has been fixed:
  \begin{itemize}
    \item handle the computation for the turbulent behavior when
      Reynolds numbers belongs to the interval $[2000, 4000]$. This
      fix is required for a correct computation of gas velocity in
      pipes;
    \item fix an error pointed out by Terranova for network topologies
      where gas setup nodes are placed higher respect load nodes. The
      fix has been accepted by Terranova Software itself as valid.
  \end{itemize}
  The previous points allow a refactoring of small chunks of code in
  order to make it perform better.
  
\item[water context enhancement] in order to support our work, we
  enhance the engine toward handling the water context too,
  specializing some behaviors extending the original code base. This
  required not much effort since the pretty code structure (only a new
  class has been created) and the solid theoretical foundation
  proposed by Fabio, which simplify a lot this enhancement.  The main
  new concept introduced in this activity is that of ``tank'', a node
  with the special capability to change its water level during time,
  giving to the entire system a dynamic aspect which isn't present in
  gas networks.
  \newpage
\item[scheduling the engine] in order to ``program'' fixed network
  events (such as a do load variations for a node, switch off a
  pipe...), we built a scheduler for the water context which allow to
  run the fluid dynamic engine several times driven by the set of
  scheduled events. A prototype of the scheduler is completely
  implemented in \emph{Smalltalk} and tested against a general, yet
  quite real, town water network specification.
  
\item[Oris 1.0 maintenance] we've started a maintenance process for
  Oris 1.0 project, in order to give it a second life by restoring a
  classic building tool chain toward Linux, Windows platforms, 32/64
  bit architectures. We restored the original workspace and change it
  in order to make it compile, updating references to newly compiled
  libraries for code written in C++: in a first check did with
  Prof. Vicario, we validated four main components, namely the Petri Net
  Editor, the Trace Extractor, the Trace Analyzer and the (token game)
  simulator.
\end{description}

\begin{tabular}{ l c l }
  written by Massimo Nocentini,  &  & approved by Enrico Vicario,  \\
  Dr. in Computer Science & & Full Professor \\
  \url{massimo.nocentini@gmail.com} &  & \url{enrico.vicario@unifi.it} \\
\end{tabular}

\end{document}
